% Document class and basic packages
\documentclass[a4paper]{article}

% Essential packages
\usepackage{fullpage}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{textcomp}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[hidelinks]{hyperref}
\usepackage[left=2cm, right=2cm, top=2cm]{geometry}
\usepackage{longtable}

% Document settings
\textheight=10in
\pagestyle{empty}
\raggedright

% Custom commands
\def\bull{\vrule height 0.8ex width .7ex depth -.1ex}

\newcommand{\area}[2]{
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder}{
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header}[1]{
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer}[3]{
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact}[3]{
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses}[4]{
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school}[4]{
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}

% Begin document
\begin{document}
    \vspace*{-40pt}

    % Header section
    \vspace*{-2pt}
    \begin{center}
        {\Huge \scshape {Isaque Carlos da Silva Melo}}\\
        \vspace*{2pt}
        \ {Desenvolvedor Web}\\
        \vspace*{2pt}
        \href{mailto:isaquecaralos2016@gmail.com}{isaquecaralos2016@gmail.com} | \href{tel:+55 11 67136275}{++55 11 67136275}\\
        \vspace*{4pt}
        \textbf{\href{linkedin.com/in/isaquecarlos}{Linkedin | }}\textbf{\href{github.com/IsaqueCarlos28 }{GitHub | }}
        % \textbf{\href{https://x.com/andreeliasdev}{X |}}
        % \textbf{\href{https://www.andreelias.dev}{Portfolio}}\\
    \end{center}

    % Summary section
    \header{Summary}
    \vspace{2mm}
    Full-stack engineer with 5+ years of experience optimizing performance and scalability for web applications. Contributed to engineering at a Y Combinator startup, launched SaaS products generating \$30K+ revenue, and built a 3D multiplayer game that reached 1M+ plays.
    \vspace{2mm}

    % Experience section
    \header{Experience}
    \vspace{2mm}

       \textbf{Creem}\textbf{ | Founding GTM Engineer} \hfill  Oct 2025 - Jan 2026\\
    \vspace{-3mm}
   \begin{itemize} \itemsep -3pt
    \item Worked on-site in Tallinn to scale a Merchant of Record platform.
    \item Launched growth initiatives including automated video onboarding, SDKs, and new integrations.
    \item Improved authentication and developer experience to reduce friction for new merchants.
    \item Contributed to consistent \textasciitilde15\% month-over-month GMV growth.
\end{itemize}

           \textbf{Rocketseat}\textbf{ | Educator } \hfill  Sep 2024 - Today\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
    \item Recorded courses focused on Micro SaaS, product development, and applied AI.
    \item Participated in live sessions and mentorships with thousands of developers.
    \item Helped students bridge the gap between software engineering and entrepreneurship.
\end{itemize}

    \textbf{Resquared}\textbf{ | Full-Stack Software Engineer} \hfill  Sep 2023 - Nov 2024\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Optimized front-end performance through React component optimization and implementing code splitting, reducing initial load and unnecessary re-renders.
        \item Developed and deployed new features to enable customers to send high-volume email batches efficiently.
    \end{itemize}

    \textbf{Kalidash}\textbf{ | Senior Software Engineer } \hfill  Nov 2022 - Nov 2024\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Built a full-featured platform for collecting data from third-party APIs and delivering meaningful insights for decision-making.
        \item Mentored 2 junior developers, reducing their time-to-productivity through structured training and code reviews.
    \end{itemize}

    \textbf{ICE Play}\textbf{ | Cofounder \& Software Engineer} \hfill  Dec 2021 - Nov 2022\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Developed a scalable course platform with integrated video streaming, leveraging AWS services to deliver seamless learning experiences.
        \item Played a key role as cofounder in shaping product strategy, business planning, and growth initiatives.
    \end{itemize}

    \textbf{Hotmart}\textbf{ | Data Analyst Intern} \hfill  Dec 2020 - Dec 2021\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Developed high-performance SQL queries to support business analysis, streamlining data retrieval and enabling faster, more informed decision-making.
        \item Used Python to develop data analysis workflows focused on affiliate programs, enabling the identification of performance trends, user behavior, and revenue opportunities.
    \end{itemize}

    % Projects section
    \header{Projects}
    \vspace{2mm}

    \textbf{Court Kings 3D}\text{ | 3D Multiplayer Game } \hfill  Jun 2023\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Achieved 1M+ plays optimizing game performance to run at 60 FPS on low-end devices.
        \item Implemented efficient WebSocket communication reducing latency and enabling real-time multiplayer features.
    \end{itemize}

    \textbf{LoveYuu}\text{ | Micro SaaS for Couples}\hfill  Sep 2024\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Generated \$30,000+ USD in revenue through organic traffic.
        \item Achieved 99\% user satisfaction rate through intuitive UI/UX design and responsive customer support.
    \end{itemize}

    \textbf{YouTube Channel}\hfill  Oct 2024\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Grew channel to 21,000+ subscribers with 500K+ views.
        \item Secured brand sponsorships through high-quality technical content and engaged community.
    \end{itemize}

    \textbf{Next.js SaaS Template}\hfill  Nov 2024\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Generated \$5,000+ USD in revenue through organic sales.
        \item Reduced development time for new SaaS projects through reusable components and documentation.
    \end{itemize}

    \textbf{Jesus In Chat}\hfill  Jan 2025\\
    \vspace{-3mm}
    \begin{itemize} \itemsep -3pt
        \item Achieved \$3000+ USD in Revenue through personalized biblical Q\&A responses.
        \item Processed 300000+ messages with 99.9\% accuracy using optimized WhatsApp API integration.
    \end{itemize}
    \vspace{1mm}

    % Skills section
    \header{Skills}
    \vspace{2mm}
    \begin{longtable}{p{4cm}p{12cm}}
        Programming Languages: & Typescript, Python, C, Swift (learning) \\
        Frontend: & React, Next.js, Tailwind, Three.js, Solid.js, Zustand, Redux \\
        Databases \& Servers: & PostgreSQL, MySQL, MongoDB, WebSockets \\
        Platforms \& Others: & AWS, Firebase, Growth (GTM), Game Development \\
    \end{longtable}
    \vspace{1mm}

    % Education section
    \header{Education}
    \vspace{2mm}
    \textbf{Universidade Federal de Viçosa}\hfill Florestal, Brazil\\
    Bachelor Computer Science (Incomplete) \hfill Jan 2017 - Dec 2021\\

\end{document}